Bioinformatics Assignment 3

### 2016-03-14 bioinformatics/latex/a5.tex
finish bi a5.pdf

@@

\section{Problem 3: }
Do this last

@@

\section{Problem Six: ChipSeq}

\end{document}

>>>>

\begin{align*}
  \frac{0.001 * 10}{1} \leq \frac{0.001 * 10}{2} \leq \frac{0.005 * 10}{3} \leq
  \frac{0.01 * 10}{4} \leq \frac{0.01 * 10}{5} \leq \frac{0.05 * 10}{6} \leq
  \frac{0.02 * 10}{7} \le \frac{0.03 * 10}{8} \leq \frac{0.2 * 10}{9} \leq
  \frac{0.5 * 10}{10}\\
\end{align*}

\begin{align*}
  0.01 - 0.005 - \frac{0.0}5{3} \leq
  \frac{0.01 * 10}{4} \leq \frac{0.01 * 10}{5} \leq \frac{0.05 * 10}{6} \leq
  \frac{0.02 * 10}{7} \le \frac{0.03 * 10}{8} \leq \frac{0.2 * 10}{9} \leq
  \frac{0.5 * 10}{10}\\
\end{align*}

@@

\section{Problem 3: }
We download the sonic hedgehog gene and run \texttt{hmmscan} to find the location of likely domains.
We use Pfam database human domains from Lab 9 to do this. When we run \texttt{hmmscan} we get
the following (trimmed) results:

\begin{verbatim}
#                                      -------------- this domain ---
# target name        accession   tlen  i-Evalue  score  bias   description of target
#------------------- ---------- -----  -------- ------ ----- -----------------------
HH_signal            PF01085.15   161   2.7e-85  283.8   0.0   Hedgehog amino-terminal
Hint                 PF01079.17   214   7.8e-72  241.1   0.0   Hint module
Peptidase_M15_3      PF08291.8    111     0.001   19.0   0.0   Peptidase M15
Hint_2               PF13403.3    143         3    8.0   0.0   Hint domain
\end{verbatim}

Here we see the top two domains, the ``Hedgehog amino-terminal'' and ``Hint module'' have
pretty small E-values compared to the other two. The tlens are similar for all of these
domains, so we can compare their E-values and say the top two domains are significant and
the bottom two aren't.\\

@@

\section{Problem Five: jnet domains}
Here we use the \texttt{jnet} program to find the predicted secondary structure of human
beta-defensin-1 sequence. Here are the results:\\

\begin{verbatim}
 RES	: MRTSYLLLFTLCLLLSEMASGGNFLTGLGHRSDHYNCVSSGGQCLYSACPIFTKIQGTCYRGKAK
 ALIGN	: ---HHHHHHHHHHHHHHHH----EEE---------EEE-----EE-E----EEEE----------
 CONF	: 83146888899999876405884010246668753030587632101255231211200023322
 FINAL	: ---HHHHHHHHHHHHHHHH----EEE---------EEE-----EEEE----EEEE----------
\end{verbatim}

Here we see there is likely a large alpha-helix (H) near the N-terminus and 4
beta-sheets evenly spaced throughout.\\

This compares pretty well to the RCSB structure prediction, which predicts an
alpha-helix near the N-term and three alpha-helices evenly spaced through the
protein.\\

\section{Problem Six: ChIPSeq}
To find the p-value of the ChIPSeq peak we are given, we use the following formula:\\

\begin{align*}
  \mbox{p-val} &= 1 - F(N_{ChIP}-1,N_{ChIP}+N_{cont}, 0.5)\\
  \mbox{p-val} &= 1 - F(46, 65, 0.5)\\
  &= 0.000211 = 2.1*10^{-4}\\
\end{align*}

This is a fairly small p-value, which means this is likely a legitimate peak.\\
\end{document}
